---
title: "Homework Week 6 - Winners"
author: "Bailey Jørgensen"
format: html
editor: visual
---

```{r}
# Load libraries
library(duckdb)
library(dplyr)
library(dbplyr)
```


```{r}
# Connect to the duckbd 
conn <- dbConnect(duckdb::duckdb(), "database/database.db")
```


```{r}
# Take a look at all the tables available to us
db_tables <- tbl(conn, sql("SHOW TABLES")) %>% collect()
print(db_tables)
```
```{r}
bird_nests <- tbl(conn, "bird_nests")
head(bird_nests)
```


```{r}
# Load the Bird_eggs table
bird_eggs <- tbl(conn, "Bird_eggs")

# Take a look at the egg table
head(bird_eggs)
```
```{r}
# Create personnel table
personnel_table <- tbl(conn, "Personnel")

# Take a look at the personnel table
head(personnel_table)

```

## Looking at these rows, I think we need to join the Personnel table (which has the full names and the name abbreviations associated) to the bird_eggs table (which has Egg_num category we need to count the eggs measured). In order to do that though, we also need the bird_egg table, which has the abbreviation name of observer and the nest_id, which can link the two tables together. 


```{r}
# Make the connections
bird_nests <- tbl(conn, "bird_nests")
personnel_table <- tbl(conn, "Personnel")
bird_eggs <- tbl(conn, "Bird_eggs")

# Join tables together into 1
egg_nest_person <- bird_nests |> 
  inner_join(bird_eggs, by = "Nest_ID") |> 
  inner_join(personnel_table, by = c("Observer" = "Abbreviation"))

# Aggregate egg count per observer
top_observers <- egg_nest_person |> 
  group_by(Name) |> 
  summarise(total_eggs = n()) |> 
  arrange(desc(total_eggs)) |> 
  head(3)

# Display the final query
show_query(top_observers)

# Print results
top_observers

```

## The code above prints out the desired results according to instructions! 

Vanessa Loverti (163)
Dylan Kessler (87)
Richard Lanctot (50)

```{r}
# Display the final query
show_query(top_observers)
```
It looks like it did not create a temp table, but managed to do everything in one query. It used LIMIT 3 at the end of the query to limit the results to just the tree top winners. 


